Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-11-03 Supplemental-Material-B-Annotated-Analysis.Rmd
methods and results re-run

# young medical professionals
dtMedical <- list(
  raw.pre = c(),
  raw.post = c(),
  raw.daily = c()
)
```

@@

To be done after preregistration.

```{r cleanMedical}
# TBD
```

@@

@@

To be done after preregistration.

```{r newVarsMedical}
# TBD
```

>>>>

# young medical professionals
dtMedical <- list(
  raw.eligibility = read.csv("data/S3_Medical/raw/AOTM_Eligibility.csv"),
  raw.pre = read.csv("data/S3_Medical/raw/AOTM_Pre.csv"),
  raw.post = read.csv("data/S3_Medical/raw/AOTM_Post.csv"),
  raw.daily = read.csv("data/S3_Medical/raw/AOTM_Daily.csv")
)
```

@@

For the medical professionals sample data was, again, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement. We combine the three individual surveys into one large dataframe. We exclude our own test data. We also reformat missing values and format core ID variables.  
<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtMedical_' list.

```{r cleanMedical}
# our own test IDs
ownIDs <- c(
  "test_LeonieXXXSklxecPLW0-FBPM4796o3pUwUhAY5jb9KGw8jQsKxWmGpa1Jiy", 
  "test_MaxXXXtOp_5dTNefIq0yKXtXt2IN6eEKxeHoPY9mlyvdsqPpLp1B0NGg4UL",
  "test_JannisXXXBsNqk62fOpX6chbd2tMWPptUdjjnhAqnQ3uBqckZ7gLIEoPlfZ",
  "quaintLeopardCatXXXAJ9cfSj-_SZLwNwMDxv_xv_iyr1Bg5YFLTlYdrjW0UXZY",
  "blue-eyedIndianElephantXXXLf5zPMpQCDGS3umFzIj-YVky7ivTItvvozW49m"
)

# Prepare dfs for Cleaning
df.pre <- dtMedical$raw.pre %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!session %in% ownIDs) %>% # remove our own test
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.post <- dtMedical$raw.post %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>% 
  filter(!is.na(session)) %>% # remove own test runs
  filter(!session %in% ownIDs) %>% # remove our own test
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  #filter(!is.na(ended)) %>% # remove all who never finished [disabled because only relevant if data is missing]
  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.daily <- dtMedical$raw.daily %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!session %in% ownIDs) %>% # remove our own test
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  #filter(!is.na(ended)) %>% # remove all who never finished [disabled because only relevant if data is missing]
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

# add to list
dtMedical$clean <- dfCombined

@@

For the student sample, the data transformation stage had five main aims:

@@

For the medical professional sample, the data transformation stage had five main aims:

1. We first create person, survey type, and measurement ID variables.   
2. We then created indices of scales. Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).   
3. We cluster mean-center key variables within participants.   
4. Finally, we calculated several basic participant summaries (averages across all measurement occasions).

```{r newVarsMedical}
df <- dtMedical$clean

# order time
df$TID <-
  factor(df$date_period, levels = unique(dtMedical$raw.daily$date_period))
df$TIDnum <- as.numeric(df$TID) # get numeric TID

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("RelatednessSelf", "RelatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <-
  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
  NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
           na.rm = TRUE)
# Pro-Sociality
df$ProSo <-
  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = T)
# Anti-Sociality
df$AntiSo <-
  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)

```

```{r newVarsStudents}
